Mixed effect tweedie model in TMB

### 2020-02-06 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
updates to temp and do prediction grids

```{r}
m_temp_rw <- sdmTMB(d_trawl,
  temperature_c ~ 0 + as.factor(year),
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, include_spatial = TRUE, # changed AR1_field to true
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE
)

@@

```{r}
plot_map_raster <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    coord_fixed()+
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank())
}

@@

```{r}
p_nd1 <- p_nd %>% filter(ssid!=16) %>% filter(ssid!=4)
st_1n3 <- plot_map_raster(p_nd1, "epsilon_st") +
  ggtitle("Spatiotemporal random effects") +
  facet_wrap(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +
  labs(fill = "epsilon") + 
  gfplot::theme_pbs() + 
  theme(
  legend.position = "none", 
  axis.title.x = element_blank(), axis.title.y = element_blank())
st_1n3
```

```{r}
p_nd4 <- p_nd %>% filter(ssid==4) #%>% filter(ssid!=4)
st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  #ggtitle(" ") +
  facet_wrap(~year) +
     scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +
          labs(fill = " ") + 
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = c(.85,.15))
st_4
```

>>>>

```{r}
m_temp_rw <- sdmTMB(d_trawl,
  temperature_c ~ 0 + as.factor(year), #+ DOY_scaled + as.factor(ssid)
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, # changed AR1_field to true
  include_spatial = TRUE, 
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE
)

@@

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_revised")

plot_map_raster <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    coord_fixed()+
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank())
}

@@

```{r}
p_nd1 <- p_nd %>% filter(ssid!=16) %>% filter(ssid!=4)
st_1n3 <- plot_map_raster(p_nd1, "epsilon_st") +
  ggtitle("Spatiotemporal random effects") +
  facet_wrap(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), trans = sqrt,
    na.value = "red") +
  labs(fill = "epsilon") + 
  gfplot::theme_pbs() + 
  theme(
  legend.position = "none", 
  axis.title.x = element_blank(), axis.title.y = element_blank())

png(
  file = "figs/temp-predictions-1n3.png", 
  res = 400,
  units = "in",
  width = 8, 
  height = 8
) 
st_1n3
dev.off()

```{r}
p_nd4 <- p_nd %>% filter(ssid==4) #%>% filter(ssid!=4)
st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  #ggtitle(" ") +
  facet_wrap(~year) +
     scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), trans = sqrt,
    na.value = "red") +
          labs(fill = " ") + 
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = c(.85,.15))
st_4
```

### 2020-02-06 analysis/tmb-sensor-explore/3-fit-do.Rmd
updates to temp and do prediction grids

```{r}
p_nd4 <- p_nd %>% filter(ssid==4) %>% filter(year!=2016)
pred_4 <- plot_map_raster(p_nd4, "do_est") +
  scale_fill_viridis_c(labels = labels, breaks = c(0,2,4,6,8), limits = c(0, 9), na.value = "red")+
  facet_wrap(~year) +
  labs(fill = "ml/L DO") +
  #ggtitle(" ")+ 
  theme(legend.position = "none")
pred_4
```

@@

```{r}
p_nd4 <- p_nd %>% filter(ssid==4) %>% filter(year!=2016)
st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  #ggtitle(" ") +
  facet_wrap(~year) +
  scale_fill_gradient2( high = "Steel Blue 4",
  low = "Red 3", limits = c(-0.5,0.5)) +
          labs(fill = "epsilon") + 
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = "none")
st_4
```

>>>>

```{r}
p_nd4 <- p_nd %>% filter(ssid==4) #%>% filter(year!=2016)
pred_4 <- plot_map_raster(p_nd4, "do_est") +
  scale_fill_viridis_c(labels = labels, breaks = c(0,2,4,6,8), limits = c(0, 9), na.value = "red")+
  facet_wrap(~year) +
  labs(fill = "ml/L DO") +
  #ggtitle(" ")+ 
  theme(legend.position = "none")
pred_4
```

@@

```{r}
p_nd4 <- p_nd %>% filter(ssid==4) #%>% filter(year!=2016)
st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  #ggtitle(" ") +
  facet_wrap(~year) +
  scale_fill_gradient2( high = "Steel Blue 4",
  low = "Red 3", limits = c(-0.5,0.5)) +
          labs(fill = "epsilon") + 
gfplot::theme_pbs() + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = "none")
st_4
```
